Supporting Information: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-05-01 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Small reference changes and removing unused figs

\externaldocument[M-]{ms}

@@

  Analogous to Figure~\ref{M-fig:anticorrelated_hops} of the main text,
  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.

>>>>

\externaldocument[M-]{Final_Draft_JCTC}

@@

  Figure~\ref{fig:anticorrelated_hops} demonstrates that all solutes exhibit the
  same kind of anti-correlated hopping and trapping behavior.
